---
title: "SolarEnergyDataExploration"
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(readxl)
library(dplyr)
library(FactoMineR)
library(ggplot2)
library(corrr)
library(factoextra) #Easy PCA plots and visualization
library(FactoMineR) #PCA and factor analysis functions  
library(ggplot2) #Enhanced data visualization
library(dplyr) #Data manipulation
library(gridExtra) #Arranging multiple plot grids
library(gt) # For creating beautiful tables
library(tidyr)
library(dplyr)
library(ggplot2)
library(lubridate)
library(viridis)
library(rmarkdown)
library(plotly)
library(shinyalert)
library(timetk)

load("df_numericVars.RData")
load("solarData.RData")
load("data.RData")
load("~/Project-2024/solarProject/solarGripObject.RData")
```

# Abstract

This report offers a detailed analysis of daily solar energy data collected from 64 distinct locations within our facility over one year. Each location, including SKH 1(MANDIR), N1, R1, and W1&2(A), provides insights into spatial orientation and operational characteristics affecting solar energy utilization. Functional areas like N4 AAC& DAC, N5&NAS(CANTEEN), and organizational units such as LADIES SEVADAL, RADIO SAI AUDIO, and specialized facilities (PLANETORIUM & STP &PSN1) are also examined for their energy consumption patterns.

Key findings underscore the following:

-   **Spatial Dynamics:** Locations such as `SKH 1(MANDIR)` and `N1` exhibit strong correlations in solar energy readings, suggesting shared solar exposure and proximity.

-   **Functional Insights:** Areas like `N4 AAC& DAC` and `N5&NAS(CANTEEN)` demonstrate distinctive energy consumption patterns linked to operational schedules and functional demands.

-   **Organizational Impacts:** Units like `RADIO SAI AUDIO` and `LADIES SEVADAL` show synchronized energy consumption behaviors, potentially due to shared operational schedules or infrastructure.

Additionally, Principal Component Analysis (PCA) identifies dominant factors driving energy variations across these locations and units. `PC1` captures broad variance across most traits, while `PC2` highlights secondary influences observed in `N8`, `S3`, and `PSN STP`. This multidimensional approach provides a nuanced understanding of energy efficiency and optimization potentials within our facility.

# Mapping Solar Synergy: Insights from Correlation Analysis Across Multiple Locations

## Correlation Analysis

To understand the relationships between the solar energy readings at different locations, we performed a correlation analysis. The correlation matrix provides insights into how the solar energy data from various locations are related to each other.

#### Highly Correlated Pairs

1.  **SKH 1 (MANDIR) and SKH 2 (0.911**\*):\*\* A strong positive correlation suggests that solar energy readings at SKH 1 (MANDIR) and SKH 2 move together. This could be due to their proximity or similar exposure to sunlight.

2.  **N1 and N4 AAC & DAC (0.945**\*):\*\* The high correlation indicates that the energy readings at N1 and N4 AAC & DAC are closely related, possibly due to similar operational schedules or environmental factors affecting both areas.

3.  **N4 AAC & DAC and R3 (0.953**\*):\*\* This strong correlation signifies that the solar energy readings at N4 AAC & DAC and R3 are almost directly proportional, indicating a likely operational or locational connection between these areas.

4.  **N5 & NAS (CANTEEN) and N6 (0.843**\*):\*\* The correlation between these areas is strong, suggesting that their solar energy consumption or generation patterns are similar.

5.  **W1 & 2 (A) and W1 & 2 (B) (0.898**\*):\*\* This high correlation indicates that the energy readings in both segments of W1 & 2 are highly synchronized, which could be due to similar usage patterns or solar exposure.

6.  **RADIO SAI AUDIO and RADIO SAI VIDEO (0.968**\*):\*\* The almost perfect correlation between these two areas implies that their energy consumption or generation patterns are nearly identical, likely due to similar operational schedules or equipment.

#### Moderately Correlated Pairs

1.  **N1 and N3 & N4 (0.862**\*):\*\* This correlation suggests a strong relationship between the solar energy readings of these areas, although not as strong as the highest correlations observed.

2.  **R1 and N9 & N9 A (0.836**\*):\*\* This indicates a significant correlation, suggesting a shared factor influencing the solar energy readings in these areas.

3.  **W3 & 4 (A) and W3 & 4 (B) (0.928**\*):\*\* A strong correlation between the segments of W3 & 4 suggests similar patterns in solar energy readings, likely due to similar solar exposure or usage.

4.  **SHANTHI BHAVAN and LADIES SEVADAL (0.729**\*):\*\* This correlation is indicative of a moderate relationship between the solar energy readings at these locations, possibly due to shared operational schedules or proximity.

#### Weakly Correlated Pairs

1.  **S3 and S5 (0.446**\*):\*\* This weaker correlation suggests that while there is some relationship between the solar energy readings in these areas, it is not as strong as others.

2.  **SSS RJY 2 and SSS HOSTEL EB2 (0.031):** The near-zero correlation indicates no significant relationship between the solar energy readings at these locations, suggesting they operate independently of each other.

#### Negative or No Correlation

1.  **SSS RJY 2 and N2 (0.336**\*):\*\* While still positive, the correlation is lower compared to other pairs, indicating a weaker relationship between the solar energy readings at these locations.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
cor_mat_allan <- function(df, type = "pearson", digits = 3, decimal.mark = ".", use = "all", show_significance = TRUE, replace_diagonal = FALSE, replacement = "") {
  # Check arguments
  stopifnot({
    is.numeric(digits)
    digits >= 0
    use %in% c("all", "upper", "lower")
    is.logical(replace_diagonal)
    is.logical(show_significance)
    is.character(replacement)
  })
  # We need the Hmisc package for this
  require(Hmisc)
  
  # Retain only numeric and boolean columns
  isNumericOrBoolean = vapply(df, function(x) is.numeric(x) | is.logical(x), logical(1))
  if (sum(!isNumericOrBoolean) > 0) {
    cat('Dropping non-numeric/-boolean column(s):', paste(names(isNumericOrBoolean)[!isNumericOrBoolean], collapse = ', '), '\n\n')
  }
  df = df[isNumericOrBoolean]
  
  # Transform input data frame to matrix
  x <- as.matrix(df)
  
  # Run correlation analysis using Hmisc package
  correlation_matrix <- Hmisc::rcorr(x, type = type)
  R <- correlation_matrix$r # Matrix of correlation coefficients
  p <- correlation_matrix$P # Matrix of p-value
  
  # Transform correlations to specific character format
  Rformatted = formatC(R, format = 'f', digits = digits, decimal.mark = decimal.mark)
  
  # If there are any negative numbers, we want to put a space before the positives to align all
  if (sum(R < 0) > 0) {
    Rformatted = ifelse(R > 0, paste0(' ', Rformatted), Rformatted)
  }
  
  # Add significance levels if desired
  if (show_significance) {
    # Define notations for significance levels; spacing is important.
    stars <- ifelse(is.na(p), "   ", ifelse(p < .001, "***", ifelse(p < .01, "** ", ifelse(p < .05, "*  ", "   "))))
    Rformatted = paste0(Rformatted, stars)
  }
  # Build a new matrix that includes the formatted correlations and their significance stars
  Rnew <- matrix(Rformatted, ncol = ncol(x))
  rownames(Rnew) <- colnames(x)
  colnames(Rnew) <- paste(colnames(x), "", sep = " ")
  
  # Replace undesired values
  if (use == 'upper') {
    Rnew[lower.tri(Rnew, diag = replace_diagonal)] <- replacement
  } else if (use == 'lower') {
    Rnew[upper.tri(Rnew, diag = replace_diagonal)] <- replacement
  } else if (replace_diagonal) {
    diag(Rnew) <- replacement
  }
  
  return(Rnew)
}

correlation_matrix = cor_mat_allan(df[,-c(1,2)]) %>% 
  as.data.frame() %>% 
  gt(rownames_to_stub = TRUE) %>% 
  tab_header(
    title = md("**Correlation Matrix**"),
    subtitle = "Package used: Hmisc; PB-Perfect"
  ) %>% 
  tab_source_note(
    source_note = "Source: PCA - Data analysis"
  ) %>% 
  tab_options(
    heading.subtitle.font.size = 12,
    heading.align = "left",
    table.border.top.color = "red",
    column_labels.border.bottom.color = "red",
    column_labels.border.bottom.width = px(3)
  ) %>% 
  opt_stylize(style = 6, color = "cyan") %>% 
  tab_options(table.width = pct(80)) %>% 
  tab_footnote(
    footnote = "Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1"
  )

correlation_matrix

```

### Insights about the Facility Based on the Correlation Analysis

The correlation analysis of the solar energy data reveals several insights about the facility:

#### Operational and Locational Similarities

1.  **Proximity and Similar Exposure**

    -   Areas like SKH 1 (MANDIR) and SKH 2, and W1 & 2 (A) and W1 & 2 (B) exhibit high correlations, indicating that these areas are likely close to each other and experience similar solar exposure. This suggests that their design and layout might have been planned to optimize solar energy utilization collectively.

2.  **Shared Operational Schedules**

    -   The strong correlation between RADIO SAI AUDIO and RADIO SAI VIDEO implies that these areas likely operate simultaneously or have similar energy usage patterns. This could be due to synchronized operational schedules or shared infrastructure.

3.  **Similar Usage Patterns**

    -   N1 and N4 AAC & DAC, and N4 AAC & DAC and R3 show high correlations, suggesting that these areas might have similar energy consumption patterns. This could be because of similar activities or processes happening in these areas.

#### Energy Management and Optimization

4.  **Energy Consumption Patterns**

    -   The correlation between N5 & NAS (CANTEEN) and N6 indicates that the canteen and adjacent areas might have synchronized energy usage, perhaps due to peak dining hours aligning with other activities in N6. Understanding these patterns can help in managing peak loads and improving energy efficiency.

5.  **Centralized Energy Usage**:

    -   The high correlation between various sections, such as W1 & 2 (A) and W1 & 2 (B), and W3 & 4 (A) and W3 & 4 (B), suggests that these areas might be part of larger centralized zones with similar energy demands. This centralization can be leveraged to optimize energy distribution and reduce wastage.

#### Independent Operations

6.  **Independent Areas**:

    -   Areas like SSS RJY 2 and SSS HOSTEL EB2 show near-zero correlation, indicating independent operations and possibly different energy requirements. This independence can be beneficial for creating targeted energy-saving strategies for each unique area.

#### Infrastructure and Design

7.  **Infrastructure Planning**:

    -   The observed correlations suggest that the facility’s design incorporates clusters of areas with similar energy profiles, allowing for more streamlined energy management. This planned layout can be further optimized based on detailed correlation insights to enhance solar energy efficiency.

8.  **Potential for Energy Sharing**:

    -   High correlations among certain areas imply that energy sharing or redistribution mechanisms can be implemented. For instance, during periods of high solar generation, surplus energy can be redirected to areas with similar usage patterns to maximize efficiency.

## Covariance Matrix Analysis

```{r, echo=FALSE,warning=FALSE, message=FALSE}
# Function for covariance matrix
covariance_table=cov(df[,-c(1,2)])%>%round(2)%>%as.data.frame()%>%gt( rownames_to_stub = TRUE) %>%tab_header(
  title = md("**Covariance Matrix**"),
  subtitle = "Package used : agricolae; PB-Perfect"
)%>%tab_source_note(
  source_note = "Source: JBS Research Lab"
)%>%
  tab_options(
    heading.subtitle.font.size = 12,
    heading.align = "left",
    table.border.top.color = "red",
    column_labels.border.bottom.color = "red",
    column_labels.border.bottom.width= px(3)
  )%>%opt_stylize(style = 6, color = "cyan")%>%
  tab_options(table.width = pct(80))

covariance_table
```

The covariance matrix analysis helps us understand the variability and linear relationships between different pairs of variables (solar energy readings in this case). Below is a detailed analysis of the key pairs from the covariance matrix:

#### Highly Correlated Pairs

##### SKH 1 (MANDIR) and SKH 2 (Covariance: 370.06)

-   **Interpretation**: This strong positive covariance suggests that variations in solar energy readings at SKH 1 (MANDIR) and SKH 2 are closely linked, possibly due to similar environmental conditions or proximity.

##### N1 and N4 AAC & DAC (Covariance: 765.26)

-   **Interpretation**: High covariance indicates that changes in solar energy readings at N1 and N4 AAC & DAC are strongly related. This might be due to shared operational schedules or environmental factors.

##### N4 AAC & DAC and R3 (Covariance: 419.61)

-   **Interpretation**: A high covariance between these locations suggests a direct relationship, indicating that their solar energy readings increase or decrease together, likely due to operational or locational connections.

##### Moderately Correlated Pairs

##### N1 and N3 & N4 (Covariance: 741.65)

-   **Interpretation**: This significant covariance indicates a strong relationship between the solar energy readings of these areas, highlighting possible operational or environmental similarities.

##### R1 and N9 & N9 A (Covariance: 402.63)

-   **Interpretation**: A significant covariance suggests that R1 and N9 & N9 A share a factor influencing their solar energy readings, potentially indicating synchronized energy consumption patterns.

##### W3 & 4 (A) and W3 & 4 (B) (Covariance: 674.81)

-   **Interpretation**: Strong covariance between these segments suggests similar patterns in solar energy readings, likely due to similar solar exposure or usage.

### Weakly Correlated Pairs

#### S3 and S5 (Covariance: 183.15)

-   **Interpretation**: This lower covariance suggests that while there is some relationship between the solar energy readings in these areas, it is not as strong as others.

#### SSS RJY 2 and SSS HOSTEL EB2 (Covariance: 70.71)

-   **Interpretation**: The low covariance indicates no significant relationship between the solar energy readings at these locations, suggesting independent operation.

#### Negative or No Correlation

#### SSS RJY 2 and N2 (Covariance: 342.17)

-   **Interpretation**: While still positive, the covariance is lower compared to other pairs, indicating a weaker relationship between the solar energy readings at these locations.

## Eigenvalues and Eigenvectors Interpretation

```{r, echo=FALSE, warning=FALSE, message=FALSE}
eigen_table=function(data){
  library(factoextra)
  library(FactoMineR)
  library(gt)
  data=data[,-c(1,2)]
  data=na.omit(data)
  
  pc=PCA(data,scale.unit = T, graph = F)
  x=get_eigenvalue(pc)
  x=t(x)
  rownames(x)=c("Eigen Value","Variance %", "Cumulative Variance %")
  colnames(x)=paste("PC",1:ncol(x),sep = "")
  x=round(x,2)
  
  y=eigen(cor(data))$vectors
  colnames(y)=paste("PC",1:ncol(x),sep = "")
  rownames(y)=colnames(data)
  
  x=rbind(x,y)
  
  x=as.data.frame(x)
  x=round(x,2)
  
  
  grp=c(rep("Eigen values and Variance %",3),rep("Eigenvectors",nrow(y)))
  
  x_out=cbind(grp,x)
  x=cbind(x,grp)
  
  
  x=x%>%gt(groupname_col = "grp", rownames_to_stub = TRUE)%>%
    tab_header(
      title = md("**Eigenvalues and Eigenvectors**"),
      subtitle = "Package used : agricolae; PB-Perfect")%>%
    tab_source_note(source_note = "Source: JBS Reserach Lab")%>%
    tab_options(
      heading.subtitle.font.size = 12,
      heading.align = "left",
      table.border.top.color = "red",
      column_labels.border.bottom.color = "red",
      column_labels.border.bottom.width= px(3)
    )%>%opt_stylize(style = 6, color = "cyan")%>%
    tab_options(table.width = pct(80))
  return(x)
  
}


eig_table=eigen_table(data)
eig_table
```

#### Overview

Principal Component Analysis (PCA) was performed to reduce the dimensionality of the dataset while retaining as much variance as possible. The PCA results include eigenvalues, variance percentages, and eigenvectors for 61 principal components (PCs).

#### Eigenvalues

Eigenvalues represent the amount of variance captured by each principal component. Higher eigenvalues indicate that the corresponding principal component captures more variance in the data.

-   **PC1** has an eigenvalue of 45.16, capturing the most significant portion of the variance.

-   **PC2** has an eigenvalue of 2.29, capturing a much smaller portion of the variance.

-   Subsequent PCs have decreasing eigenvalues, indicating that each captures progressively less variance.

#### Variance Explained

The variance percentage shows the proportion of the dataset's total variance that is captured by each principal component.

-   **PC1** explains 74.04% of the variance, indicating it is the most influential component.

-   **PC2** explains 3.75% of the variance.

-   **PC3** to **PC61** each explain progressively smaller percentages of the variance, with **PC61** explaining only 0.01%.

#### Cumulative Variance

The cumulative variance percentage indicates the total variance explained by the first n principal components.

-   The first two PCs together explain 77.78% of the variance.

-   The first three PCs explain 80.23% of the variance.

-   The cumulative variance continues to increase, with the first 61 PCs explaining 100% of the variance.

#### **Patterns of Loadings: Clusters and Groups**

-   **PC1 Loadings Similarity**: Facilities like N1, N2, N3, N4, and others have similar loadings on PC1 (around -0.23 to -0.28). This suggests that these facilities are influenced by a common underlying factor, which could be related to overall demand, efficiency, or usage trends. For example, if PC1 represents overall demand, an intervention to boost demand could impact these facilities similarly.

-   **Distinct Loadings on Subsequent PCs**: Facilities like N8 have notably different loadings on PC2 compared to others, indicating unique characteristics or issues specific to these facilities. Investigating these unique loadings can help identify specific operational or structural differences.

#### **Influence of Minor Principal Components**

-   **Contribution of Smaller PCs**: Even though PCs beyond PC10 contribute less to the total variance, their loadings can still reveal critical insights. For instance, a facility with high loading on PC20 might exhibit a specific pattern that, although not dominant in the overall data, could be crucial for niche operational insights.

#### **Impact of Negatively Loaded Variables**

-   **Negative Loadings on PC1**: The negative loadings on PC1 for most facilities suggest that as PC1 scores increase, the associated factor (e.g., an operational efficiency metric) decreases. Understanding what this negative loading represents can help in identifying critical operational inefficiencies.

-   **Comparative Analysis**: Facilities with less negative loadings might be performing better in the context of PC1-related factors. These could be benchmark facilities for best practices.

#### **Interpreting Specific Component Contributions**

-   **PC2 and PC3 Nuances**: Facilities with high positive or negative loadings on PC2 and PC3 might have specific characteristics or challenges. For example:

    -   **N8’s High Loading on PC2**: Suggests unique operational patterns. This facility might have specific issues or strengths related to the factor captured by PC2.

    -   **Negative Loadings on PC3**: For some facilities like R1, negative loadings could indicate specific vulnerabilities or operational weaknesses in the dimension represented by PC3.

#### **Eigenvalues and Scree Plot Insights**

-   **Sharp Decline in Eigenvalues**: The sharp drop from PC1 to PC2 suggests that the dataset is heavily influenced by the first principal component. This can be interpreted as a strong common trend influencing most of the data.

-   **Long Tail of Minor PCs**: The slow decline after PC10 implies a "long tail" of smaller, yet potentially meaningful components. These minor PCs might capture subtle but important variations or anomalies in the data that major PCs miss.

#### **Potential for Dimensionality Reduction**

-   **Effective Dimensionality Reduction**: Given that the first 10 PCs capture nearly 89% of the variance, the dimensionality of the dataset can be significantly reduced without substantial loss of information. This can simplify data analysis and visualization, making it easier to focus on key operational metrics.

#### **Operational Implications of PCA Results**

-   **Resource Allocation**: Facilities with similar loadings across major PCs might benefit from similar resource allocation strategies, while those with divergent loadings might require tailored approaches.

-   **Strategic Planning**: The principal components can be used to inform strategic planning by highlighting which operational aspects (captured by PCs) should be prioritized for different facilities.

#### **Hidden Relationships and Interactions**

-   **Inter-Facility Relationships**: Similar loadings on minor PCs might indicate hidden relationships or interactions between specific facilities. Identifying and exploring these could uncover cooperative opportunities or shared challenges.

-   **Temporal Dynamics**: If data over time is included, changes in loadings can reveal dynamic shifts in facility operations, helping in predicting future trends and preparing proactive measures.

#### Key Insights from PCA Trait Statistics

```{r, echo=FALSE, warning=FALSE, message=FALSE}
var_stats=function(data){
  library(FactoMineR)
  library(dplyr)
  
  res.pca=get_pca_var(PCA(data))
  res.pca=lapply(res.pca, as.data.frame)
  res.pca=lapply(res.pca, function(x){colnames(x)=c(paste("PC",1:ncol(x),sep = ""));x})
  res.pca=lapply(res.pca, round,2)
  
  cor_pca=res.pca$cor
  cos_pca=res.pca$cos2
  contrib_pca=res.pca$contrib
  
  grp=("Correation between PCs and Traits")
  cor_pca=cbind(cor_pca,grp)
  grp=("Quality of representation of Traits on PCs")
  cos_pca=cbind(cos_pca,grp)
  grp=c("Contributions(%) of the Traits to the Principal Components")
  contrib_pca=cbind(contrib_pca,grp)
  
  res=rbind(cor_pca, cos_pca, contrib_pca)
  x=res%>%gt(groupname_col = "grp", rownames_to_stub = TRUE)%>%
    tab_header(
      title = md("**PCA - Trait statistics**"),
      subtitle = "Package used : agricolae; PB-Perfect")%>%
    tab_source_note(source_note = "Source: JBS Research Lab")%>%
    tab_options(
      heading.subtitle.font.size = 12,
      heading.align = "left",
      table.border.top.color = "red",
      column_labels.border.bottom.color = "red",
      column_labels.border.bottom.width= px(3)
    )%>%opt_stylize(style = 6, color = "cyan")%>%
    tab_options(table.width = pct(80))
  
  return(x)
  
}

variable_stats = var_stats(data)
variable_stats
```

#### Correlation between PCs and Traits

1.  **PC1 Dominance**:

    -   **High Correlation**: Most traits have a high correlation with PC1 (values around 0.9). This suggests that PC1 explains a significant portion of the variance in the data, indicating a common factor affecting all these traits.

    -   **Traits with High PC1 Correlation**: N1, N2, N3 & N4, N4 AAC & DAC, N6, N7, R2, R3, W 5&6 (B), W9, S1 A, S7to8, LADIES SEVADAL, and others.

2.  **PC2 Variation**:

    -   **Notable Positive Correlation**: Some traits such as N8 (0.42), S3 (0.53), and WC (0.17) have a higher correlation with PC2, indicating a secondary factor influencing these traits differently from PC1.

    -   **Negative Correlation**: SIC (-0.31), NIC (-0.31), and PSN STP (-0.45) have a negative correlation with PC2, suggesting an inverse relationship to the factor represented by PC2.

3.  **PC3 to PC5 Contributions**:

    -   **Lower Impact**: Traits generally show lower correlations with PC3, PC4, and PC5, indicating these components explain less variance compared to PC1 and PC2.

    -   **Exceptions**: Traits like PSN STP (0.34 for PC3, 0.36 for PC4) and SSS HOSTEL EB2 (0.61 for PC3) show higher correlations with these components, indicating specific factors influencing these traits.

#### Quality of Representation of Traits on PCs

1.  **Strong Representation on PC1**:

    -   **High Values**: Traits like N4 AAC & DAC (0.94), N6 (0.90), R3 (0.93), W 5&6 (B) (0.95), and S1 A (0.92) have high values on PC1, suggesting they are well-represented by the first principal component.

    -   **Broad Influence**: This broad influence indicates that PC1 captures the major variations in the dataset.

2.  **Moderate to Low Representation on PC2 to PC5**:

    -   **Lower Values**: Traits generally have lower values on PC2 to PC5, indicating these components capture more specific, less dominant variations in the data.

#### Contributions (%) of the Traits to the Principal Components

1.  **Significant Contributors to PC1**:

    -   **Key Traits**: N4 AAC & DAC (2.07%), R3 (2.05%), W 5&6 (B) (2.11%), and LADIES SEVADAL (2.07%) contribute significantly to PC1, highlighting their importance in the overall variance explained by this component.

2.  **Distinctive Contributions to Other PCs**:

    -   **PC2**: N8 (7.86%), S3 (12.15%), PSN STP (8.67%), and SSS RYY 2 (9.74%) are notable for their higher contributions to PC2.

    -   **PC3 and Beyond**: Specific traits like S3 (4.77% to PC3) and SSS HOSTEL EB2 (25.35% to PC3) show significant contributions, indicating their unique influence captured by these components.

#### Insights on Specific Areas

1.  **High Performing Areas**:

    -   **N1 to N7**: Consistently show high correlations and contributions, indicating robust performance in these regions.

    -   **W5&6 and S1 A**: High values and contributions suggest strong performance and significant variance explanation in these areas.

2.  **Areas with Specific Influences**:

    -   **PSN STP**: Notable contributions to PC3 and PC4 suggest specific factors affecting this area uniquely.

    -   **SSS HOSTEL EB2**: High contribution to PC3 (25.35%) highlights unique influences or variations in this area.

# Temporal Trends and Variability in Solar Energy Data across Multiple Locations

### Analysis of Daily and Weekly Readings

In this section, we present two heatmaps to visualize the daily and weekly average unit readings across various areas. These visualizations provide insights into temporal patterns and variations in unit measurements.

#### Daily Readings Heatmap

The heatmap depicts the daily & Weekly average unit readings for different areas respectively.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
selected_data_daily <- selected_data_long %>%
  mutate(Week = lubridate::floor_date(DATE, unit = "day")) %>%  
  group_by(Week, Areas) %>%
  summarise(Units = mean(Units))  

# Plotting the weekly heatmap with inverted viridis color palette
ggplot(selected_data_daily, aes(x = Week, y = Areas, fill = Units)) +
  geom_tile(color = "white") +
  scale_fill_viridis(option = "plasma", trans = "reverse") +  # Invert viridis color scale
  labs(
    title = "Daily Solar Readings",
    x = "Daily",
    y = "Areas",
    fill = "Units"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 1)
  )


```

```{r, echo=F,warning=F, width = 20, message=FALSE}
# Plotting the weekly heatmap with inverted viridis color palette
ggplot(selected_data_weekly, aes(x = Week, y = Areas, fill = Units)) +
  geom_tile(color = "white") +
  scale_fill_viridis(option = "plasma", trans = "reverse") +  # Invert viridis color scale
  labs(
    title = "Weekly Solar Readings",
    x = "Week",
    y = "Areas",
    fill = "Units"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 1)
  )

```

```{r, echo=F, warning=FALSE, message=FALSE}
library(dplyr)
library(timetk)

# Convert DATE to Date type if not already done
solarData_long <- solarData_long %>%
  mutate(DATE = as.Date(DATE))

# Select 6 random areas
set.seed(123)  # Setting seed for reproducibility
selected_areas <- solarData_long %>%
  distinct(Areas) %>%
  sample_n(6) %>%
  pull(Areas)

# Filter the dataset for the selected areas
filtered_data <- solarData_long %>%
  filter(Areas %in% selected_areas)

# Create faceted time series plot using timetk
filtered_data %>%
  plot_time_series(
    .date_var = DATE,
    .value = Units,
    .facet_var = Areas,
    .facet_ncol = 2,
    .facet_scales = "free"
  )


```
